### 2018-03-17 papers.tex
Add Ryan's paper
Add Michael's paper
papers.tex: Track the papers received thus far

\addproceedings{Portrait of Markov}

\addtrack
	[\scalebox{0.1}{\includegraphics{tracks/bear}}\scalebox{0.1}{\includegraphics{tracks/bear}}\scalebox{0.1}{\includegraphics{tracks/bear}}\scalebox{0.1}{\includegraphics{tracks/bear}}]
	{One Track to Rule Them All}{One Track to Find Them}

\addpaper
	{Is this the shortest SIGBOVIK paper?}
	{Dicong Qiu}
	{}
	{SIGBOVIK_2018_paper_1}
	{0cm}
	{}
\addpaper
	{Cubic partitioning of simultaneous antipodal 4-corner-day time spaces}
	{R.\ Welch and G.\ Ray}
	{}
	{SIGBOVIK_2018_paper_2}
	{0cm}
	{}
\addpaper
	{Sublinear colorings of 3-colorable graphs in linear time}
	{Thomas Tseng}
	{}
	{SIGBOVIK_2018_paper_3}
	{0cm}
	{}
\addpaper
	{mallocd:\ designing a garbage-free nosql data store}
	{igor}
	{}
	{SIGBOVIK_2018_paper_4}
	{0cm}
	{}
\addpaper
	{Ritwik density estimation and analysis using real techniques}
	{Ritwik Gupta, Ritwik Das, and Ritwik Rajendra}
	{}
	{SIGBOVIK_2018_paper_5}
	{0cm}
	{}
\addpaper
	{Towards a formalization of Claude Shannon's masters thesis}
	{andrewtron3000}
	{}
	{SIGBOVIK_2018_paper_7}
	{0cm}
	{}
\addpaper
	{PSYCHO:\ PerSonalitY CHaracterizatiOn of artificial intelligence}
	{Achal Dave and Rohit Girdhar}
	{}
	{SIGBOVIK_2018_paper_8}
	{0cm}
	{}
\addpaper
	{Heuristic Ordered-Word Longform Obfuscation, Normally Generated, Creating Abstract
	Nominalizations In Monogrammatic Arrangement Keeping Expected Maximum Yield:\ Study Infers
	Greater Breadth Over Vocabularic Initialization Key Property Regarding Extended
	Sesquipedalian Entries; Notably The Abecedarian Tactics Include Overelaboration, Neologisms,
	Textual Interpretations Twisting Lexical Entries By Eliciting Full Online Resources
	Explaining Possible Exchanges; Often Potential Logorrheic Excesses Require Eventual
	Alternate Listing (Instantiating Zeugma); Energetically Iterating Text Strains Jocularity
	Under Starting Thesis Allocating Humor Until Grand Exit After Conclusion Reaches Obvious
	Nadir Yattering Meaninglessly}
	{Luke Breitfeller}
	{}
	{SIGBOVIK_2018_paper_9}
	{0cm}
	{}
\addpaper
	{The NUGGET non-linear piecewise activation}
	{Stephen Merity}
	{}
	{SIGBOVIK_2018_paper_10}
	{0cm}
	{}
\addpaper
	{CommieCoin:\ Seizing the means of crypto-production}
	{Marx van Raasveldt \textit{et al.}}
	{}
	{SIGBOVIK_2018_paper_11}
	{0cm}
	{}
\addpaper
	{WordTeX:\ A WYSIPCTWOTCG typesetting tool}
	{Tom Wildenhain}
	{}
	{SIGBOVIK_2018_paper_12}
	{0cm}
	{}
\addpaper
	{Transactional memory concurrency verification with Landslide}
	{Ben Blum}
	{}
	{SIGBOVIK_2018_paper_13}
	{0cm}
	{}

@@

\addpaper
	{Automating art snobbiness:\ Dead duck or phoenix?}
	{Dion Ysus and Oscar I.\ Hernandez}
	{}
	{SIGBOVIK_2018_paper_14}
	{0cm}
	{}
\addpaper
	{GradCoin:\ A poor-to-poor electronic cash transfer system}
	{Siddhant Jain}
	{}
	{SIGBOVIK_2018_paper_15}
	{0cm}
	{}
\addpaper
	{Alternary operators:\ Alternative ternary operators}
	{Jim McCann; Your Name Here; and Your Name Here, Evan}
	{}
	{SIGBOVIK_2018_paper_16}
	{0cm}
	{}
\addpaper
	{A definitely not cherry-picked rhetorical analysis of programming languages reviews}
	{Hannah G.\ Ringler and Stefan Muller}
	{}
	{SIGBOVIK_2018_paper_17}
	{0cm}
	{}
\addpaper
	{The fluint8 software integer library}
	{Jim McCann and Tom Murphy VII}
	{}
	{SIGBOVIK_2018_paper_18}
	{0cm}
	{}
\addpaper
	{bashcc:\ Multi-prompt one-shot delimited continuations for Bash}
	{Spencer Baugh and Dougal Pugson}
	{}
	{SIGBOVIK_2018_paper_19}
	{0cm}
	{}
\addpaper
	{COBOLd:\ Gobblin' up COBOL bugs for fun and profit}
	{squaresLab and Mr.\ squaresLab SpouseMan}
	{}
	{SIGBOVIK_2018_paper_20}
	{0cm}
	{}
\addpaper
	{Toward a historically faithful performance of the piano works of Anton\'in Qwe\v{r}t\'y}
	{William Gunther and Brian Kell}
	{}
	{SIGBOVIK_2018_paper_21}
	{0cm}
	{}
\addpaper
	{Chess circuits}
	{Ross Dempsey, Sydney Timmerman, and Karl Osterbauer}
	{}
	{SIGBOVIK_2018_paper_22}
	{0cm}
	{}
\addpaper
	{This grad student studied parapsychology---and you won't believe what he found}
	{David Edelstein}
	{}
	{SIGBOVIK_2018_paper_23}
	{0cm}
	{}
\addpaper
	{Academic Advancement Advice:\ Author Articles as A.\ A.}
	{A.\ A.}
	{}
	{SIGBOVIK_2018_paper_24}
	{0cm}
	{}

>>>>

\addproceedings{You know what's a neat form of literature?}

\addtrack
	{Theory}{\textit{Bottles}}
\addpaper
	{Sublinear colorings of 3-colorable graphs in linear time}
	{Thomas Tseng}
	{}
	{SIGBOVIK_2018_paper_3}
	{0cm}
	{}
\addpaper
	{Cubic partitioning of simultaneous antipodal 4-corner-day time spaces}
	{R.\ Welch and G.\ Ray}
	{}
	{SIGBOVIK_2018_paper_2}
	{0cm}
	{}
\addpaper
	{Chess circuits}
	{Ross Dempsey, Sydney Timmerman, and Karl Osterbauer}
	{}
	{SIGBOVIK_2018_paper_22}
	{2cm}
	{}

\addtrack
	{Cryptocurrencies}{\textit{A Dream}}
\addpaper
	{GradCoin:\ A poor-to-poor electronic cash transfer system}
	{Siddhant Jain}
	{}
	{SIGBOVIK_2018_paper_15}
	{0cm}
	{}
\addpaper
	{CommieCoin:\ Seizing the means of crypto-production}
	{Marx van Raasveldt \textit{et al.}}
	{}
	{SIGBOVIK_2018_paper_11}
	{0cm}
	{}

\addtrack
	{Stochastic Processes}{\textit{Portrait of Markov}}
\addpaper
	{Ritwik density estimation and analysis using real techniques}
	{Ritwik Gupta, Ritwik Das, and Ritwik Rajendra}
	{}
	{SIGBOVIK_2018_paper_5}
	{0cm}
	{}

\addtrack
	{Ayyy Eye}{\textit{Open Your Third Eye}}
\addpaper
	{PSYCHO:\ PerSonalitY CHaracterizatiOn of artificial intelligence}
	{Achal Dave and Rohit Girdhar}
	{}
	{SIGBOVIK_2018_paper_8}
	{0cm}
	{}
\addpaper
	{The NUGGET non-linear piecewise activation}
	{Stephen Merity}
	{}
	{SIGBOVIK_2018_paper_10}
	{0cm}
	{}

\addtrack
	{Parapsychology}{\textit{Get Out of My Head}}
\addpaper
	{This grad student studied parapsychology---and you won't believe what he found}
	{David Edelstein}
	{}
	{SIGBOVIK_2018_paper_23}
	{0cm}
	{}

\addtrack
	{Art}{\textit{The Way They Fly}}
\addpaper
	{Automating art snobbiness:\ Dead duck or phoenix?}
	{Dion Ysus and Oscar I.\ Hernandez}
	{}
	{SIGBOVIK_2018_paper_14}
	{0cm}
	{}
\addpaper
	{Toward a historically faithful performance of the piano works of Anton\'in Qwe\v{r}t\'y}
	{William Gunther and Brian Kell}
	{}
	{SIGBOVIK_2018_paper_21}
	{0cm}
	{}
\addpaper
	{WordTeX:\ A WYSIPCTWOTCG typesetting tool}
	{Tom Wildenhain}
	{}
	{SIGBOVIK_2018_paper_12}
	{0cm}
	{}

@@

\addtrack
	{Systems}{\textit{Wheel}}
\addpaper
	{The fluint8 software integer library}
	{Jim McCann and Tom Murphy VII}
	{}
	{SIGBOVIK_2018_paper_18}
	{0cm}
	{}
\addpaper
	{mallocd:\ designing a garbage-free nosql data store}
	{igor}
	{}
	{SIGBOVIK_2018_paper_4}
	{0cm}
	{}

\addtrack
	{Debugging}{\textit{Amy Likes Spiders}}
\addpaper
	{COBOLd:\ Gobblin' up COBOL bugs for fun and profit}
	{squaresLab and Mr.\ squaresLab SpouseMan}
	{}
	{SIGBOVIK_2018_paper_20}
	{0cm}
	{}
\addpaper
	{Transactional memory concurrency verification with Landslide}
	{Ben Blum}
	{}
	{SIGBOVIK_2018_paper_13}
	{0cm}
	{}

\addtrack
	{Programming Languages}{\textit{Save Me}}
\addpaper
	{Dead programming}
	{Michael Coblenz}
	{}
	{SIGBOVIK_2018_paper_25}
	{0cm}
	{}
\addpaper
	{Alternary operators:\ Alternative ternary operators}
	{Jim McCann; Your Name Here; and Your Name Here, Evan}
	{}
	{SIGBOVIK_2018_paper_16}
	{0cm}
	{}
\addpaper
	{bashcc:\ Multi-prompt one-shot delimited continuations for Bash}
	{Spencer Baugh and Dougal Pugson}
	{}
	{SIGBOVIK_2018_paper_19}
	{0cm}
	{}
\addpaper
	{Towards a formalization of Claude Shannon's masters thesis}
	{andrewtron3000}
	{}
	{SIGBOVIK_2018_paper_7}
	{0cm}
	{}

\addtrack
	{Metaresearch}{\textit{Literature Club}}
\addpaper
	{Heuristic Ordered-Word Longform Obfuscation, Normally Generated, Creating Abstract
	Nominalizations In Monogrammatic Arrangement Keeping Expected Maximum Yield:\ Study Infers
	Greater Breadth Over Vocabularic Initialization Key Property Regarding Extended
	Sesquipedalian Entries; Notably The Abecedarian Tactics Include Overelaboration, Neologisms,
	Textual Interpretations Twisting Lexical Entries By Eliciting Full Online Resources
	Explaining Possible Exchanges; Often Potential Logorrheic Excesses Require Eventual
	Alternate Listing (Instantiating Zeugma); Energetically Iterating Text Strains Jocularity
	Under Starting Thesis Allocating Humor Until Grand Exit After Conclusion Reaches Obvious
	Nadir Yattering Meaninglessly}
	{Luke Breitfeller}
	{}
	{SIGBOVIK_2018_paper_9}
	{0cm}
	{}
\addpaper
	{Transparency in research}
	{Ryan Kavanagh}
	{}
	{SIGBOVIK_2018_paper_26}
	{0cm}
	{}
\addpaper
	{Academic Advancement Advice:\ Author Articles as A.\ A.}
	{A.\ A.}
	{}
	{SIGBOVIK_2018_paper_24}
	{0cm}
	{}
\addpaper
	{A definitely not cherry-picked rhetorical analysis of programming languages reviews}
	{Hannah G.\ Ringler and Stefan Muller}
	{}
	{SIGBOVIK_2018_paper_17}
	{0cm}
	{}
\addpaper
	{Is this the shortest SIGBOVIK paper?}
	{Dicong Qiu}
	{}
	{SIGBOVIK_2018_paper_1}
	{0cm}
	{}
